How to Avoid OOTA Without Really Trying

### 2024-09-03 paper/ootavacuous.tex
ootavacuous: Fix obsolete thread0/thread1 uses for Listing 1
Reported-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Recall the Simple OOTA example in Listing~\ref{lst:Simple OOTA} on
page~\pageref{lst:Simple OOTA},
in which \co{thread1()} loads the value of \co{x} and stores it in
\co{y} while \co{thread2()} does the reverse.
A sufficiently perverse globally optimizing loose C++ compiler might
transform that program to the following before translating it into
machine code: \\
% Constructed by hand.
{
\small
\begin{tabular}{r|l|l}
% & \multicolumn{1}{c}{P0} & \multicolumn{1}{c}{P1} \\
% \hline
1. &
\texttt{~~int r1 = 42} &
	\texttt{~~int r2 = 42} \\
2. &
\texttt{~~y = r1} &
	\texttt{~~z = r2} \\
\end{tabular}
} \\
The loads previously on lines~6 and~12 have been replaced by constants.
Such a transformation complies with the loose C++ standard,
even though the resulting executable file would produce an unintuitive
OOTA outcome every time it runs!

>>>>

Recall the Simple OOTA example in Listing~\ref{lst:Simple OOTA} on
page~\pageref{lst:Simple OOTA},
in which P0 loads the value of \co{x} and stores it in \co{y} while P1
does the reverse.
A sufficiently perverse globally optimizing loose C++ compiler might
transform that program to the following before translating it into
machine code: \\
% Constructed by hand.
{
\small
\begin{tabular}{r|l|l}
% & \multicolumn{1}{c}{P0} & \multicolumn{1}{c}{P1} \\
% \hline
1. &
\texttt{~~int r1 = 42} &
	\texttt{~~int r2 = 42} \\
2. &
\texttt{~~y = r1} &
	\texttt{~~z = r2} \\
\end{tabular}
} \\
The loads previously on lines~6 and~12 have been replaced by constants.
Such a transformation complies with the loose C++ standard,
even though the resulting executable file would produce an unintuitive
OOTA outcome every time it runs!
